---
title: "My amazing report 😎"
format: closeread-html
editor: visual
---

### Setup

Let's load the libraries and load our data. We'll call the data set `power_temp`:

```{r}
library(tidyverse)
power_temp <- read_csv("power-temperature-threesites.csv")
```

::::: cr-section
## The U-curve

Demand for electricity is lower on mild days (in the middle) and higher on cold or hot (left or right) days. Here's an example of one site, the Dock Area: @cr-onesite

::: {#cr-onesite}
```{r}
power_temp |>
  filter(site == "DA") |>
  ggplot() +
    aes(x = tmax, y = demand, colour = working) +
    geom_point(size = 2) +
    facet_wrap(vars(name)) +
    scale_colour_manual(values = c(
      "Weekday" = "#880000",
      "Weekend" = "#00ccff"
    )) +
    scale_x_continuous(labels = scales::label_number(suffix = " °C")) +
    scale_y_continuous(labels = scales::label_number(suffix = " MW")) +
    theme(plot.title = element_text(size = rel(1.5))) +
    labs(
      x = "Daily temperature peak",
      y = "Electricity demand",
      title = "Electricity and temperature",
      subtitle = "People use less electricity on mild days, when it's\nnot too hot and not too cold."
      )
```
:::

In fact, we see this relationship in most places. Here are two others: @cr-threesites

::: {#cr-threesites}
```{r}
ggplot(power_temp) +
  aes(x = tmax, y = demand, colour = working) +
  geom_point(size = 2) +
  facet_wrap(vars(name)) +
  scale_colour_manual(values = c(
    "Weekday" = "#880000",
    "Weekend" = "#00ccff"
  )) +
  scale_x_continuous(labels = scales::label_number(suffix = " °C")) +
  scale_y_continuous(labels = scales::label_number(suffix = " MW")) +
  theme(plot.title = element_text(size = rel(1.5))) +
  labs(
    x = "Daily temperature peak",
    y = "Electricity demand",
    title = "Electricity and temperature",
    subtitle = "People use less electricity on mild days, when it's\nnot too hot and not too cold."
    )
```
:::

But there are some interesting differences between sites too: @cr-threesites

-   In Port Melbourne, we see demand fall substantially on [weekends]{style="background-color: #00ccff; color: white;"} (in blue) compared to [weekdays]{style="background-color: #880000; color: white;"} (red). This doesn't happen as much at the two other sites. @cr-threesites

-   In Northcote, electricity demand increases much more at extreme temperatures than other sites.
:::::
