---
format:
  revealjs: 
    theme: [default, style/style.scss]
    highlight-style: github
    width: 1400
    fig-width: 15
---

## Title here {.hleft .center style="font-size: 150%;"}

### And a subtitle

James Goldie

# Hi! {#section-aqua}

## A bit about me

# Storytelling fundamentals

## Audience, message and medium

## Audience

## Message

## Medium

## Anything else?

# Using Quarto for storytelling

## What is Quarto?

# Example 1<br>Telling stories with graphics

## Example 1

Your data is **electricity demand** and **temperature** at **3 inner Melbourne sites**:


:::{style="font-size: 48%;"}
```{ojs}
powerTemp = FileAttachment("data/power-temperature-threesites.csv").csv({ typed: true })

Inputs.table(powerTemp)
```
:::

## A basic chart

```{r}
#| library: slides-setup
library(tidyverse)
library(here)
```

```{r}
#| label: basic-chart
power_temp <- read_csv(here("data", "power-temperature-threesites.csv"))

ggplot(power_temp) +
  aes(x = tmax, y = demand, colour = working) +
  geom_point(size = 2) +
  facet_wrap(vars(name)) +
  labs(
    x = "2m air temperature [°C]",
    y = "Electricity demand [MW]",
    title = "Electricity and temperature")
```

What stories could we tell with this data?

What improvements could we make?

# Scrollytelling with Closeread

# Example 2<br>Using Closeread

# Wrapup {#section-carbon}

## Use Closeread, win prizes

Andrew Bray (my collaborator on Closeread) and I have teamed up with data science company **Posit** to run the **Closeread Prize**.

https://posit.co/blog/closeread-prize-announcement

Entries close Jan 5th  
[(we just extended the contest!)]{.small .deemph}

## Thanks! Questions?

{{< iconify fa6-brands:bluesky >}} [@jamesgoldie.dev](https://bsky.app/profile/jamesgoldie.dev)

{{< iconify bi:mastodon >}} [@jimjamslam@aus.social](https://aus.social/@jimjamslam@aus.social)

{{< iconify bi:linkedin >}} [linkedin.com/in/jamesgoldie](https://www.linkedin.com/in/jamesgoldie)
